Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-05 manuscript.tex
Move more figures
Move more figures.
JGCD sucks

\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
\begin{figure}[htbp]
    \centering
    \input{tikz/castalia_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
\end{figure}
The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.

@@

For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
The original unit cube is composed of \num{8} vertices and \num{12} faces.
The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
The two large triangular faces are divided into a number of smaller triangular faces.
Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.45\textwidth]{figures/original_cube.jpg}}~
    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.45\textwidth]{figures/remesh_cube.jpg}}
    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
\end{figure}

>>>>

\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
\begin{figure}[htbp]
    \centering
    \input{castalia_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
\end{figure}
The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.

@@

For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
The original unit cube is composed of \num{8} vertices and \num{12} faces.
The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
The two large triangular faces are divided into a number of smaller triangular faces.
Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.45\textwidth]{original_cube.jpg}}~
    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.45\textwidth]{remesh_cube.jpg}}
    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
\end{figure}
